---
title: "RMarkdown Tips and Tricks"
author: "Terence McSweeney"
date: "18/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Useful tips and tricks page from this book about papaja:

[papaja book manual](https://crsh.github.io/papaja_man/introduction.html)

[Tips and tricks section](https://crsh.github.io/papaja_man/tips-and-tricks.html)

# Some recommended packages:

`citr`: Insert Markdown Citations

`remedy`: Keyboard shortcuts for Markdown formatting

`wordcount`: Word counts and readability statistics

`statcheck`: Extract Statistics from Articles and Recompute p Values

`retractcheck`: Check DOIs in a paper for retractions

# Really nice handout on RMarkdown:

https://libscie.github.io/rmarkdown-workshop/handout.html

# Another good tutorial:

https://achale.gitlab.io/tutorialmarkdownthesis/

# And another:

https://tysonbarrett.com/jekyll/update/2018/02/11/r_dissertation/

# Fantastic discussion thread full of advice:

https://community.rstudio.com/t/what-are-your-recommendations-for-thesis-writing-with-rstudio-and-rmarkdown/13576/26

# Further excellent list of resources:

https://theaknowles.com/post/ongoing-curated-list-of-useful-resources-for-writing-articles-theses-in-rmarkdown/

# Dissertation writing advice and generally nice website...

https://livefreeordichotomize.com/2018/09/14/one-year-to-dissertate/

# Series of blog posts with a nice gthub of the outpt:

https://www.rosannavanhespen.nl/thesis_in_rmarkdown/

# "thesisdown"

https://thesisdown.netlify.app/1-rmd-basics

# May be most useful for me:

https://eddjberry.netlify.app/post/writing-your-thesis-with-bookdown/

Should include session info maybe... especially if there is a lot of code?:

```{r}
devtools::session_info()
```


# How to name files:

https://speakerdeck.com/jennybc/how-to-name-files

# Nice website:

https://www.weirdfishes.blog/blog/